Discrete Quantum Theories and Computing

### 2018-04-01 dissertation.tex
dissertation.tex Acknowledgments Updating...

\begin{acknowledgments}The acknowledgments are designed to recognize
people or agencies to whom you feel grateful for any academic, technical,
financial, or personal aid in the preparation of your thesis or dissertation;
as a matter of courtesy, you would ordinarily mention the members
of your committee here, as well as institutions that provided funding,
your typist, or anyone else who helped.\end{acknowledgments}
\begin{abstract}
Our primary research interest is to build a quantum computing model
characterizing realistic quantum computers. While most of the quantum
computing models based on uncomputable numbers, that is, the continuum
of real numbers, most of the classical computers in our daily life
are digital instead of analog computers. This highlight the necessity
to investigate discrete models for quantum theory and computing. Specifically,
we start from replacing the continuum of complex numbers by the discrete
finite fields. Although we have fruitful results on their geometric
implications and computing powers, their probability models are still
not completely satisfactory. To address this issue, we further exploited
quantum interval-valued probability, and proved an imprecise version
of foundational results such as the Gleason and Kochen-Specker theorems.
\end{abstract}
\tableofcontents{}

\chapter{Introduction}

@@

\chapter{Quantum Theories and Computing over Finite Fields}

@@

\section{Irreducible Discrete $D$-dimensional States: Generalized Discrete
Bloch Sphere\label{DQCnqubitBloch.sec}}

@@

\section{Toward Discrete Quantum Probability}

@@

\chapter{Toward a Quantum Measurement Theory with Error: Quantum Interval-Valued
Probability}

>>>>

\begin{acknowledgments}Thank Prof. Andrew J. Hanson, Prof. Gerardo
Ortiz, and Prof. Amr A. Sabry for publishing three papers \cite{geometry2013,DQT2014,THOS2017}
with me. They becomes the main part of my thesis, especially most
of Chapter~\ref{chap:DQT=000026DQC} is based on ``Geometry of discrete
quantum computing''~\cite{geometry2013} and ``Discrete quantum
theories''~\cite{DQT2014}; most of Chapter~\ref{chap:DQT=000026DQC}
is based on ``Quantum Interval-Valued Probability: Contextuality
and the Born Rule'' \cite{THOS2017}. Together with Prof. Dylan Paul
Thurston and Prof. Shouhong Wang, thank you for getting together to
understand what I did and passing my dissertation proposal Spring
2017. Also, you passed my Computer Science qualified exam Spring 2016.
Especially, my survey of real computation inspires me the comparison
of quantum computer and analog computer in Chapter~\ref{chap:Introduction}.
Thank Prof. Lawrence Moss for inviting me to presented my results
in the interdisciplinary logic seminar and SICE theory seminar, co-chairing
my Tier 3 committee, and drawing my attention on Prof. Abramsky's
paper~\cite{Abramsky2012}, which inspired me to merge quantum probability
with discrete quantum theories. Thanks John Gardiner for inspiring
discussion on the difficulties merging quantum probability with discrete
quantum theories~\cite{Gardiner2014}. An improved work consists
of Sec.~\ref{sec:Toward-IVPM} \end{acknowledgments}
\begin{abstract}
Our primary research interest is to build a quantum computing model
characterizing realistic quantum computers. While most of the quantum
computing models based on uncomputable numbers, that is, the continuum
of real numbers, most of the classical computers in our daily life
are digital instead of analog computers. This highlight the necessity
to investigate discrete models for quantum theory and computing. Specifically,
we start from replacing the continuum of complex numbers by the discrete
finite fields. Although we have fruitful results on their geometric
implications and computing powers, their probability models are still
not completely satisfactory. To address this issue, we further exploited
quantum interval-valued probability, and proved an imprecise version
of foundational results such as the Gleason and Kochen-Specker theorems.
\end{abstract}
\tableofcontents{}

\chapter{Introduction\label{chap:Introduction}}

@@

\chapter{Quantum Theories and Computing over Finite Fields\label{chap:DQT=000026DQC}}

@@

\subsection{Irreducible Discrete $D$-dimensional States: Generalized Discrete
Bloch Sphere\label{DQCnqubitBloch.sec}}

@@

\section{Toward Discrete Quantum Probability\label{sec:Toward-IVPM}}

@@

\chapter{Toward a Quantum Measurement Theory with Error: Quantum Interval-Valued
Probability\label{chap:QIVPM}}
